---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# editor

Experimental!

{editor} can be used to edit scripts programmatically.

We propose the functions

* `edit_insert(path, code, before = NULL, after = NULL, style = TRUE)`
* `edit_replace(path, code, selection, style = TRUE)`
* `edit_remove(path, selection, style = TRUE)`

The position where to insert/replace/remove code is fed to the `selection`,
`before` or `after` args.

We can provide line numbers there but also by tailor made
tidy selection helpers:

* `line_matches(code, n = NULL)` to match a line's code
* `expr_defines(var, n = NULL)` to match a variable definition
* `expr_calls(fun, n = NULL)` to match a function call

By default the matches are exact (ignoring leading and trailing white spaces on both sides),
but we can use {stringr}'s modifiers like `stringr::regex()` for more flexibility.

To match a definition or call inside a function definition we can use :

* in_function(fun, selection, n = NULL)

So for example we'll do 

```
edit_insert("my_script.R", 'print("hello")', after = in_function("fun1", expr_defines("x")))`
```

And we'll have a `print("hello")` statement inserted in the `fun1()`'s definition 
right after `x` is defined.


## Installation

Install with:

```
remotes::install_github("moodymudskipper/editor")
```

## Example

```{r}
library(editor)
code <- '
# some
# comment
with_equal = c(
  1,
  2
)

with_arrow <- c(
  3,
  4
)

this <- {
  "this"
}

fun1 <- function() {
  hello <- 1
  world <- 2
  fun2 <- function() {
    hi <- 2
    again <- 3
  }
}

a(1)

ab(2)

abc(3)
'

file <- tempfile()
writeLines(code, file)
  
edit_remove(file, 2:3) # remove leading comment
edit_remove(file, expr_defines("with_equal"))
edit_remove(file, expr_defines("with_arrow"))
edit_replace(file, toupper, expr_calls(regex("a"), 3))
edit_replace(file, toupper, expr_calls("a"))
edit_remove(file, in_function("fun1", expr_defines("world")))
edit_remove(file, in_function("fun1", in_function("fun2", expr_defines("again"))))
edit_insert(file, 'print("hello")', after = expr_defines("this"))
edit_insert(file, ~paste("#", .x), before = expr_defines("this"))
edit_replace(file, toupper, line_matches('"this"'))
  
styler::style_text(readLines(file))
```

